A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-01 tex/codatadp.tex
minor
more theory

%\title{Mechanising the Metatheory of %(Many-Sorted)
%  First-Order Logic}
%\subtitle{Infrastructure and Application to Sort Encodings}
%\title{A Mechanised Metatheory of First-Order Logic \\
%  and Its Application to Sort Erasure}
\title{A Decision Procedure for (Co)datatypes in SMT Solvers}

@@

  * (co)datatype specifications:
    * N mutually recursive types (datatypes or codatatypes -- no mixture)
    * list of n constructors (n >= 1)
    * each constructor has m arguments (m >= 0)
    * each argument has a sort, which may be

>>>>

\title{A Decision Procedure for (Co)datatypes in SMT Solvers}

@@

\newcommand\keyw[1]{\textbf{#1}}

For the purposes of this paper, a (co)datatype specification consists of
$k$~mutually recursive types which are either all datatypes or all codatatypes.
Each datatype $\delta$ is equipped by $m \ge 1$ constructors, and each
constructor for $\delta$ takes $n \ge 0$ arguments, each associated with a
selector, and returns a $\delta$ value. The argument types must be either
already existing types or be one of the newly introduced (co)datatypes. The
introduced names for the (co)datatypes, the constructors, and the selectors must
be distinct with already introduced ones and among themselves. Schematically:
%
\[
\begin{aligned}[t]
(\keyw{co})\keyw{datatype}\;\,
  \delta_1 & {}=\, C_{11}\;(s_{111}{:}\; \sigma_{111}) \,\ldots\, (s_{11n_{11}}{:}\; \sigma_{11n_{11}}) & \\
           & {}\;\phantom{=\,}\;{} \smash{\,\,\vdots} \\ % {}\;\phantom{=}\llap{\ensuremath{\mid}}\; \cdots \\
           & {}\;\phantom{=\,}\llap{\ensuremath{\mid}}\; C_{1m}\;(s_{1m1}{:}\; \sigma_{1m1}) \,\ldots\, (s_{1mn_{1m}}{:}\; \sigma_{1mn_{1m}}) \\[-.5\jot]
   \smash{\vdots\,\,\,} \\[-.5\jot]
  \keyw{and}\; \,\delta_k & =\, \ldots
\end{aligned}
\]

(datatypes or codatatypes -- no mixture)
    * list of n constructors (n >= 1)
    * each constructor has m arguments (m >= 0)
    * each argument has a sort, which may be
